More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-01-29 2016-Weak-FH-Bisim/WeakBisim.tex
skype notes

\TODO{Voir ou ajouter ceci: We introduce the notation ${\displaystyle \bigotimes_{i=1}^{n} \subst{Post_i}}$ to denote a combination of multiple substitution operations}
\subsection{Weak bisimulation is an equivalence}

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta^1}_i$, $\set{\beta^2_i}$, and $\set{\beta^3_i}$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
%}
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2 \bigotimes_{i=0}^{n}\subst{\Post_i^1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}\\
\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
$

@@

\newpage
\begin{proof} Suppose we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\, l\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall p\! \in [0\ldots m_1]\,		
	P[Q]_{j_0}\!\models		
\openrule
    {
       (\set{\beta^1_p}),\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
$ 
\\
and 
 $\forall p \in [0\ldots m_2] \,\, P[Q]_{j_0}\!\models \openrule
         {
           (\set{\beta^3_p}),\Pred\,^3_p, \Post_p^3   }
         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
$\\
where for all $l\in L$:\\
$
s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^{m_1}\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land (\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2})\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}\\
\Post=(\bigotimes_{i=0}^{m_2}\Post^3_i)\subst{\Post^2}\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}
$\\
We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For each open transition  $\symb{OT}_p$ in the form: 
$P[Q]_{j_0}\!\models		
\openrule
    {
       (\set{\beta^1_p}),\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
$P\models{\openrule
			{
				(\beta^1_{p})_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred^1_p}\!',  
				{\Post^1_p}\!'}
			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
					\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} 
		Q\models{\openrule
			{
				(\beta^1_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}\!''},  
				{{\Post^1_p}\!''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}\\%\]\\
$

such that  $\Pred^1_p \iff {\Pred^1_p}\!'
		\land {\Pred^1_p}\!''\land \alpha_p=\beta_{pj_0}$, $\Post^1_p={\Post^1_p}\!'\uplus 
		{\Post^1_p}\!''$ where ${{\Post^1_p}\!''}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
Else $Q$ does not move and we have: \\
$P\models{\openrule
			{
				(\beta^1_{p})_j^{j\in (J\setminus \Holes(Q)) }, 
				{\Pred^1_p}\!',  
				{\Post^1_p}\!'}
			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{(p+1) l})^{l\in L_Q}}}
		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $

@@

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where for all $l\in L$:\\
$s_l=s_{0l} \wedge s_{{(m_1+1)}l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)}l=s'_l$\\
$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\},\quad
\displaystyle{\gamma_j}=\mybigdotcup_{i=0}^{m_1}  (\beta^1_{ij}) \dotcup  (\set{\beta^2}_i) \dotcup \mybigdotcup_{i=0}^{m_2} (\beta^3_{ij})
\\
\Pred\,'=\bigwedge_{i=0}^{m_1}
{\Pred_i^1}'\land{\Pred^2}'\bigotimes_{i=0}^{m_1}\subst{{\Post_i^1}'}\land (\bigwedge_{i=0}^{m_2}{\Pred\,^3_i}'\subst{{\Post^2}'})\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'}\\
\Post'=(\bigotimes_{i=0}^{m_2}{\Post^3_i}')\subst{{\Post^2}'}\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'}
$\\
\TODO{To check: ce n'est pas $m_1, m_2$ mais $m_1', m_2'$ such that 
 $m_1'= m_1\setminus\Holes(Q)$???}\\

@@

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of  $\tau$ action containing only one observable action.  We can decompose each subsequence $k$ of length $len$  as follows:\\
$\forall p \in [0\ldots (n'-1)] Q\models{\openrule
			{
				(\beta^1_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}''},  
				{{\Post^1_p}''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				(\beta^2)_j^{j\in J\cap\Holes(Q)}, {{\Pred^2}''},  
				{{\Post^2}''}}
				{\ostate{v_{n'l}^{l\in L_Q}} \OTarrow {\alpha_k}
				\ostate{v_{(n'+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n'+1)\ldots (len-1)]\,\, Q\models{\openrule
			{
				(\beta^3_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^3_p}''},  
				{{\Post^3_p}''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
\TODO{ Attention peut dire que ${{\Pred^1_p}''}, {{\Pred^2}''}$ are diffrent from previous one}\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we obtain the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_k)_j^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
				\ostate{v_{l}'^{l\in L_Q}}}
		}%\]
\end{mathpar}
$v_l=v_{0l} \wedge v_l'=v_{len}$\\
$\forall j \in {j\in (J\cap\Holes(Q))},\quad
\displaystyle{\gamma_{kj} }=\mybigdotcup_{i=0}^{(n'_1-1)}\!\!(\beta^1_{ij})\,\dotcup\,(\set{\beta^2})_j\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(len-1)}\!\!\!(\beta^3_{ij})
\\
\Pred_k=\!\!\bigwedge_{i=0}^{(n'_1-1)}\!\!
{\Pred_i^1}''\land{\Pred^2}''\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post_i^1}''}\land \big(\!\!\!\!\!\bigwedge_{i=(n'+1)}^{(len-1)}\!\!{\Pred^3_i}''\subst{{\Post^2}''}\big)\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post^1_i}''}\\
\Post_k=\big(\!\!\!\!\bigotimes_{i=(n'+1)}^{(len-1)}{\Post^3_i}''\big)\subst{{\Post^2}''}\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post^1_i}''}
$\\

In this case, the number of weak open transitions
might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
For  $\gamma_{j_0}=[\beta_0..\beta_n]$ we have $n$ weak open transitions  $\symb{WOT}_p$ such that $p\in [0\ldots n]$.
Therefore, we can conclude that we have forall $p\in [0\ldots n]$:  
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_p)_j^{J_p}, {\Pred_p}, {\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
\end{mathpar}
and $\displaystyle{\bigcup_{p=0}^nJ_{p}} = J\cap\Holes(Q)$, $\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}$, $\forall l\in L_Q,\, s_{0l}=s_l$, $s_{(n+1)l}=s'_l$  \\
  $\Pred \iff \Pred\,'
		\land \displaystyle{\bigvee_{p=0}^n}(\alpha_p= \beta_{pj_0}\land \Pred_p), \text{and~}
\Post=\Post\,'\uplus\biguplus_{p=0}^n
		\Post_p \quad$

>>>>

\TODO{Voir ou ajouter ceci: We introduce the notation ${\displaystyle \bigotimes_{i=1}^{n} \subst{Post_i}}$ to denote a combination of multiple substitution operations}

${\displaystyle \bigotimes_{i=0}^{n} \subst{Post_i}} = \subst{Post_n}..\subst{Post_0}$
\subsection{Weak bisimulation is an equivalence}

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta^1}_i$, $\set{\beta^2_i}$, and $\set{\beta^3_i}$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_{ik}\gets e^3_{ik}})^{k\in K_i}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
%}
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^n(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1})\land\Pred\,^2 \bigotimes_{j=0}^{n}\subst{\Post_j^1}\land (\bigwedge_{i=0}^m\Pred_i^3\bigotimes_{j=0}^{i-1}\subst{\Post_j^3}\subst{\Post^2}\bigotimes_{j=0}^{n}\subst{\Post^1_j})\\
\Post={x^3_{mk}\gets (e^3_{mk}\bigotimes_{j=0}^{m-1}\subst{\Post_j^3}\subst{\Post^2}\bigotimes_{j=0}^{n}\subst{\Post^1_j})^{k\in K_m}}
$

@@

\newpage
\begin{proof} Suppose we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\, l\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall p\! \in [0\ldots m_1]\,		
	P[Q]_{j_0}\!\models		
\openrule
    {
       (\set{\beta^1_p}),\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
$ 
\\
and 
 $\forall p \in [0\ldots m_2] \,\, P[Q]_{j_0}\!\models \openrule
         {
           (\set{\beta^3_p}),\Pred\,^3_p, \Post_p^3   }
         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
$\\
where for all $l\in L$:\\
$
s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^{m_1}\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land (\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2})\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}\\
\Post=(\bigotimes_{i=0}^{m_2}\Post^3_i)\subst{\Post^2}\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}
$\\
We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For each open transition  $\symb{OT}_p$ in the form: 
$P[Q]_{j_0}\!\models		
\openrule
    {
       (\set{\beta^1_p}),\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
$P\models{\openrule
			{
				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred^1_p}\!',  
				{\Post^1_p}\!'}
			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
					\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} 
		Q\models{\openrule
			{
				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}\!''},  
				{{\Post^1_p}\!''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}\\%\]\\
$
\TODO{from here simplify the double indices in beta and gamma}
such that  $\Pred^1_p \iff {\Pred^1_p}\!'
		\land {\Pred^1_p}\!''\land \alpha_p=\beta_{pj_0}$, $\Post^1_p={\Post^1_p}\!'\uplus 
		{\Post^1_p}\!''$ where ${{\Post^1_p}\!''}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
Else $Q$ does not move and we have: \\
$P\models{\openrule
			{
				(\beta^1_{p})_j^{j\in (J\setminus \Holes(Q)) }, 
				{\Pred^1_p}\!',  
				{\Post^1_p}\!'}
			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{(p+1) l})^{l\in L_Q}}}
		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $

@@

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where for all $l\in L$:\\
\TODO{a reprendere avec la nouvelle decomp ; add the v of visible}

$s_l=s_{0l} \wedge s_{{(m_1+1)}l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)}l=s'_l$\\
$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\},\quad
\displaystyle{\gamma_j}=\mybigdotcup_{i=0}^{m_1}  (\beta^1_{ij}) \dotcup  (\set{\beta^2}_i) \dotcup \mybigdotcup_{i=0}^{m_2} (\beta^3_{ij})
\\
\Pred\,'=\bigwedge_{i=0}^{m_1}
({\Pred_i^1}'\bigotimes_{i=0}^{i-1}\subst{{\Post_i^1}'})
\land{\Pred^2}'\bigotimes_{i=0}^{m_1}\subst{{\Post_i^1}'}\land (\bigwedge_{i=0}^{m_2}{\Pred\,^3_i}'(\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'})\subst{{\Post^2}'}(\bigotimes_{j=0}^{i-1}\subst{{\Post^3_j}'}))\\
\Post'=(\bigotimes_{i=0}^{m_2}{\Post^3_i}')\subst{{\Post^2}'}\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'}
$

@@

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.  We can decompose each of the $n$ subsequences, where sequence  $k$ has length $n_k$,  as follows:\\
$\forall p \in [0\ldots (n'-1)] Q\models{\openrule
			{
				(\beta^1_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}''},  
				{{\Post^1_p}''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				(\beta^2)_j^{j\in J\cap\Holes(Q)}, {{\Pred^2}''},  
				{{\Post^2}''}}
				{\ostate{v_{n'l}^{l\in L_Q}} \OTarrow {\alpha_k}
				\ostate{v_{(n'+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n'+1)\ldots (n_k-1)]\,\, Q\models{\openrule
			{
				(\beta^3_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^3_p}''},  
				{{\Post^3_p}''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
\TODO{ Attention peut dire que ${{\Pred^1_p}''}, {{\Pred^2}''}$ are diffrent from previous one}\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we obtain the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_k)_j^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
				\ostate{v_{l}'^{l\in L_Q}}}
		}%\]
\end{mathpar}
$\forall l. v_l=v_{0l} \wedge v_l'=v_{n_kl}$\\
$\forall j \in {j\in (J\cap\Holes(Q))},\quad
\displaystyle{\gamma_{kj} }=\mybigdotcup_{i=0}^{(n'_1-1)}\!\!(\beta^1_{ij})\,\dotcup\,(\set{\beta^2})_j\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(len-1)}\!\!\!(\beta^3_{ij})
\\
\Pred_k=\!\!\bigwedge_{i=0}^{(n'_1-1)}\!\!
{\Pred_i^1}''\land{\Pred^2}''\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post_i^1}''}\land \big(\!\!\!\!\!\bigwedge_{i=(n'+1)}^{(len-1)}\!\!{\Pred^3_i}''\subst{{\Post^2}''}\big)\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post^1_i}''}\\
\Post_k=\big(\!\!\!\!\bigotimes_{i=(n'+1)}^{(len-1)}{\Post^3_i}''\big)\subst{{\Post^2}''}\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post^1_i}''}
$\\

In this case, the number of weak open transitions
might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\

\TODO{link gamma j 0 with the alpha k ; this ises the visible abstraction and the ewautaions of 1,2,3 decomposition}
For  $\gamma_{j_0}=[\beta_0..\beta_n]$ we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [0\ldots n]$.
Therefore, we can conclude that we have for all $k\in [0\ldots n]$:  
\begin{mathpar}
Q\models{\openrule
			{
			\gamma_{kj}^{j\in J_k}, {\Pred_k}, {\Post_k}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
\end{mathpar}
and $\displaystyle{\bigcup_{p=0}^nJ_{p}} = J\cap\Holes(Q)$, $\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}$, $\forall l\in L_Q,\, s_{0l}=s_l$, $s_{(n+1)l}=s'_l$  \\
  $\Pred \iff \Pred\,'
		\land \displaystyle{\bigvee_{p=0}^n}(\alpha_p= \beta_{pj_0}\land \Pred_p), \text{and~}
\Post=\Post\,'\uplus\biguplus_{p=0}^n
		\Post_p \quad$
